### 2010-04-01 papers/icfp-2010-desc/paper_desc.tex
Desc@ICFP: fixing typos (mostly in section 3, universe of inductive types_

To give some intuition on this universe, we now turn to some
examples. For obvious pedagogical reasons, we will manually build
these descriptions. However, it should be clear that, in practice,
these definitions are automatically computed from an ML-like $\data$
definition.

@@

The $\NatSuc{\!}$ constructor is turned into a proper
$\ListCons{\!}{\!}$, taking an argument in $\V{X}$ followed by a
recursive argument. Easily, one sees that this code describes the
following functor:

@@

Again, we are at one evolutionary step away from $\ListD$. However,
instead of a single call to the induction code, we call it twice. The
interpretation of this code corresponds to the following functor:

@@

Again, this is a clear reminiscence of the sum-of-products style: we
have a finite sum of constructors. Every description can be expressed
in this style, using a singleton as a constructor if
necessary. Converselly, a tagged description can be turned into a
full-blown description. We denote $\toDesc{\V{TD}}$ the description
computed from the tagged description $\V{TD}$.

@@

For convenience, we have taken for granted the existence of $\Desc$,
as presented in Figure~\ref{fig:desc_universe}. Although it makes no
conceptual difference, the code of description should rather be read
as a specification. We promise the existence of such objects,
satisfying the typing rules. It will be the subject of
Section~\ref{sec:desc-levitate} to actually implement the
specification.

>>>>

To give some intuition on this universe, we now turn to some
examples. For obvious pedagogical reasons, we will manually build the
descriptions. However, it should be clear that, in practice, these
definitions are automatically computed from an Agda-like $\data$
definition.

@@

The $\NatSuc{\!}$ constructor is turned into a proper
$\ListCons{\!}{\!}$, taking an argument in $\V{X}$ followed by a
recursive argument. This code describes the following functor:

@@

Again, we are one evolutionary step away from $\ListD$. However,
instead of a single call to the induction code, we call it twice. The
interpretation of this code corresponds to the following functor:

@@

Again, this is a clear reminiscence of the sum-of-products style,
characterized by a finite sum of constructors. Every description can
be expressed in this style, using a singleton constructor if
necessary. Conversely, a tagged description can be turned into a
full-blown description. We denote $\toDesc{\V{TD}}$ the description
computed from the tagged description $\V{TD}$.

@@

For convenience, we have taken for granted the existence of $\Desc$,
as presented in Figure~\ref{fig:desc_universe}. Although it makes no
conceptual difference, this code should rather be read as a
specification. We promise the existence of such objects, satisfying
these typing rules. It will be the subject of
Section~\ref{sec:desc-levitate} to actually implement this
specification.
